A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface\tnoteref{t1}

### 2022-03-28 sections/conclusion/main.tex
Add example of another application of the model

The motivation behind this study has been that emergency departments are
under a lot of pressure to treat patients.
This is in practice often centrally controlled through a mechanism of some sort
of performance measure target.
This paper shows how this can negatively impact the pathway of both the
ambulance patients and the ambulance service itself.
Due to some managerial decision making that takes place at the ED, ambulances
stay blocked outside of the ED at the hospital's parking zone in an attempt
to satisfy these regulations.
The main contributions of this paper are:
\begin{itemize}
    \item A queueing model with 2 consecutive waiting spaces where one would
    serve as a parking space for the ambulances;
    \item Analytic performance measure formulas for the queueing model;
    \item A 3-player game theoretic model between the EMS and two EDs;
    \item Numerical experiments showing emergent behaviour of gaming between
    EDs and the EMS.
\end{itemize}
Although our research is motivated by the particular EMS-ED example, our 
developed modelling framework and behavioural insights has application to 
similar systems across a range of sectors and settings.
% TODO: Give example(s) of applications
% For example, the queueing model can also be used to

>>>>

The motivation behind this study has been that emergency departments are
under a lot of pressure to treat patients.
This is in practice often centrally controlled through a mechanism of some sort
of performance measure target.
This paper shows how this can negatively impact the pathway of both the
ambulance patients and the ambulance service itself.
Due to some managerial decision making that takes place at the ED, ambulances
stay blocked outside of the ED at the hospital's parking zone in an attempt
to satisfy these regulations.
The main contributions of this paper are:
\begin{itemize}
    \item A queueing model with 2 consecutive waiting spaces where one would
    serve as a parking space for the ambulances;
    \item Analytic performance measure formulas for the queueing model;
    \item A 3-player game theoretic model between the EMS and two EDs;
    \item Numerical experiments showing emergent behaviour of gaming between
    EDs and the EMS.
\end{itemize}
Although our research is motivated by the particular EMS-ED example, our 
developed modelling framework and behavioural insights has application to 
similar systems across a range of sectors and settings.
The queueing model can be applied to any setting where individuals may be
blocked on a separate queue.
An example of such setting can be any type of delivery service where customers
can purchase goods either online or walk in the store.
More specifically consider a food delivery service where customers can order
food online or walk in the store.
At busier times, the person delivering the food may be blocked outside the
restaurant in an attempt to improve the waiting times for walk-in customers.
